---
output: 
  bookdown::pdf_document2:
    includes:
      in_header: preamble.tex
    pandoc_args: 
      -  "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
    toc: no
date: "`r format(Sys.Date(),'%d %B %Y')`"
subtitle: Final survey design sub-routine (replication)
params:
  eval_1L_lgl: True
  pilot_analysis_mdl: NULL
  X: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = params$eval_1L_lgl)
```

```{r child="../Child_RMDs/Copyright.Rmd", eval=TRUE}
```

\blandscape
<!---BLOCK_LANDSCAPE_START--->

# About this code

## Motivation
This program was used to generate the final survey choice efficient design and choice cards for a Discrete Choice Experiment study that is currently being written up. Future versions of this program will include details of the parent study.

## Status
This code has been minimally adapted from when it was first applied. It has not been formatted for consistency or ease of use and a number of sections have copied almost unchanged from online examples provided by other authors to demonstrate the third party functions (in particular from the idefix package) used in this program. Future releases of this program aim to adopt a more consistent and integrated approach that should make the program easier to follow and adapt.

## Use
When using this code it is important to note that some of the steps in this program involve interactivity - they generate a prompt that a user must respond to before proceeding. Therefore, **this code should be run step by step** (i.e run one chunk at a time and do not try to run the program by knitting the R Markdown version of this code). Although it would be possible to add work-arounds to the interactivity issue, running the program by knitting the RMD version is still not recommended as it will prevent the documents generated by this program from rendering properly. 

# Install and load required libraries
If you do not already have the required libraries to run this program installed, you can do so by un-commenting and running the following lines.

```{r }
# utils::install.packages("idefix")
# utils::install.packages("kableExtra")
# utils::install.packages("knitr")
# utils::install.packages("magick")
# utils::install.packages("magrittr")
# utils::install.packages("shiny")
# utils::install.packages("stringr")
# utils::install.packages("webshot")
# utils::install.packages("xfun")
# utils::install.packages("devtools")
# devtools::install_github("ready4-dev/ready4")
# devtools::install_github("ready4-dev/ready4use")
```

Next load the libraries required to run this program.

```{r message=FALSE, warning=FALSE}
library(magrittr)
library(ready4)
library(ready4use)
```

# Create custom functions

Next we create a number of functions that we will use in subsequent parts of this program.

```{r child="../Child_RMDs/XX_Funs.Rmd", eval=TRUE}
```

# Retrieve pilot survey design
We retrieve details about the design of the pilot survey.

```{r}
X <- Ready4useRepos(dv_nm_1L_chr = "springtolife", 
                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/VGPIPS", 
                    dv_server_1L_chr = "dataverse.harvard.edu")
pilot_design_repln_ls <- ingest(X,
                                fls_to_ingest_chr = "BBB_pilot_design_repln_ls",
                                metadata_1L_lgl = F)

```

# Specify output directory
```{r}
output_dir <- "final_survey"
```

# Update survey design
We now update the survey experimental design based on analysis of pilot survey results.

```{r}
final_survey_ls <- export_eff_des(survey_features_ls,
                                   parallel = FALSE,
                                   pilot_analysis = pilot_analysis,
                                   start_des = list(pilot_survey_ls$design),
                                   output_dir = output_dir)
```

# Create choice cards for each block
We can now generate HTML choice cards for each block.

```{r warning=FALSE}
choice_cards_final_ls <- export_choice_cards(no_app_optout_ls = final_survey_ls,
                                             survey_features_ls = survey_features_ls,
                                             output_dir = output_dir)
```

# Preview survey
We can now preview all of our choice cards in an interactive Shiny app.

```{r}
preview_survey(no_app_optout_ls = final_survey_ls,
               survey_features_ls = survey_features_ls,
               pilot = F)
```

# Share work
The final step is to share our work with others in an online repository. Note, you will need to supply your own repository details to run this part of the code successfully as you will not have write permissions to the repository `X` that we specify below.

```{r eval = FALSE}
Y <- share(X,
           obj_to_share_xx = list(choice_cards_final_ls = choice_cards_final_ls,
                                  final_survey_ls = final_survey_ls),
           fl_nm_1L_chr = "BBB_final_design_repln_ls",
           description_1L_chr = "List object to help replicate pilot survey (output of dce_sa_design replication program)")
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->

