---
output: 
  bookdown::pdf_document2:
    includes:
      in_header: preamble.tex
    pandoc_args: 
      -  "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
    toc: no
date: "`r format(Sys.Date(),'%d %B %Y')`"
subtitle: Final survey design sub-routine (reproduction)
params:
  eval_1L_lgl: True
  pilot_analysis_mdl: NULL
  X: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = params$eval_1L_lgl)
```

```{r child="../Child_RMDs/Copyright.Rmd", eval=TRUE}
```

\blandscape
<!---BLOCK_LANDSCAPE_START--->

# About this code

## Motivation
This program was used to generate the final survey choice efficient design and choice cards for a Discrete Choice Experiment study that is currently being written up. Future versions of this program will include details of the parent study.

## Status
This code has been minimally adapted from when it was first applied. It has not been formatted for consistency or ease of use and a number of sections have copied almost unchanged from online examples provided by other authors to demonstrate the third party functions (in particular from the idefix package) used in this program. Future releases of this program aim to adopt a more consistent and integrated approach that should make the program easier to follow and adapt.

## Use
When using this code it is important to note that some of the steps in this program involve interactivity - they generate a prompt that a user must respond to before proceeding. Therefore, **this code should be run step by step** (i.e run one chunk at a time and do not try to run the program by knitting the R Markdown version of this code). Although it would be possible to add work-arounds to the interactivity issue, running the program by knitting the RMD version is still not recommended as it will prevent the documents generated by this program from rendering properly. 

# Install and load required libraries
If you do not already have the required libraries to run this program installed, you can do so by un-commenting and running the following lines.

```{r }
# utils::install.packages("idefix")
# utils::install.packages("kableExtra")
# utils::install.packages("knitr")
# utils::install.packages("magick")
# utils::install.packages("magrittr")
# utils::install.packages("shiny")
# utils::install.packages("stringr")
# utils::install.packages("webshot")
# utils::install.packages("xfun")
```

Next load the libraries required to run this program.

```{r message=FALSE, warning=FALSE}
library(magrittr)
```

# Create custom functions

Next we create a number of functions that we will use in subsequent parts of this program.

```{r child="../Child_RMDs/XX_Funs.Rmd", eval=TRUE}
```

```{r}
output_dir <- "final_survey"
final_survey_ls <- export_eff_des(survey_features_ls,
                                   parallel = FALSE,
                                   pilot_analysis = pilot_analysis,
                                   start_des = list(pilot_survey_ls$design),
                                   output_dir = output_dir)
```


# Create choice cards for each block
We can now generate HTML choice cards for each block.

```{r warning=FALSE}
choice_cards_final_ls <- export_choice_cards(no_app_optout_ls = final_survey_ls,
                                             survey_features_ls = survey_features_ls,
                                             output_dir = output_dir)

```

# Preview survey in Shiny App
```{r}
preview_survey(no_app_optout_ls = final_survey_ls,
               survey_features_ls = survey_features_ls,
               pilot = F)
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->

