---
title: "Prepare Workspace"
output: html_document
date: '2022-06-09'
---

# Prepare workspace

## Install and load required libraries
If you do not already have the required libraries to run this program installed, you can do so by un-commenting and running the following lines.

```{r }
# devtools::install_github("ready4-dev/ready4")
# devtools::install_github("ready4-dev/mychoice") # add lwgeom to imports
# devtools::install_github("ready4-dev/ready4use")
```

Next we load the libraries required to run this program.

```{r message=FALSE, warning=FALSE}
library(ready4)
library(ready4use)
library(mychoice)
```

```{r include=FALSE}
# PROJECT LIST
## list(dce_design_ls = list(), mdl_params_ls = list(), paths_ls = list(), preprocessing_log_ls = list(),records_ls = list())
```

## Specify whether program is a reproduction or replication
We begin by declaring whether this program is to be executed in order to reproduce the design of the original study or to replicate that study (which will produce a survey design with similar but different features). If choosing a replication, change the below setting to `F`.

```{r}
reproduce_1L_lgl <- T
```

```{r echo=FALSE, eval=!is.null(params$X)}
reproduce_1L_lgl <- params$X$reproduce_1L_lgl
```

## Specify data directories
We next specify where our input data can be located and where we wish to write our outputs to. You must supply these details or the rest of this code will not work. 

```{r eval=is.null(params$X)}
paths_ls <- list(input_data_dir_1L_chr = "PROVIDE DETAILS HERE",
                 output_data_dir_1L_chr = "PROVIDE DETAILS HERE",
                 raw_data_fl_nms_chr = "PROVIDE DETAILS HERE")
```

```{r echo=FALSE, eval=!is.null(params$X)}
paths_ls<- params$X$paths_ls
```

We also specify the online data repository. Note, if you do not have write permissions to the below repository any subsequent command to "share" outputs will not execute correctly. 

```{r}
X <- Ready4useRepos(dv_nm_1L_chr = "springtolife", 
                    dv_ds_nm_1L_chr = "https://doi.org/10.7910/DVN/VGPIPS", 
                    dv_server_1L_chr = "dataverse.harvard.edu")
```

## Reproducibility

We now set a seed to aid reproducibility.

```{r}
set.seed(1001)
```

Having set the seed, it is now likely that if you run the syntax described in this document on your own installation of R you will get identical results to those reported in this document. However, if you do not, it may be that you have a different version of R, or of some of the packages that we used to produce this analysis. We therefore save a record of the software that we have on the machine used for this analysis so this can be made available for comparisons.

```{r}
session_ls <- sessionInfo()
```

