---
title: "Replicate Pilot Analysis"
output: html_document
date: '2022-10-19'
---

```{r child=if(T){"../Child_RMDs/_Set_Up.Rmd"}else{NULL}, eval=TRUE}
```
```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Copyright.Rmd"}else{NULL}, eval=TRUE}
```

\blandscape
<!---BLOCK_LANDSCAPE_START--->

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_About_Repln_Pilot_Anlys_Code.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Prepare_Workspace.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Custom_Functions_Text.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/XX_Funs.Rmd"}else{NULL}, eval=TRUE}
```

```{r echo=FALSE}
# Make below conditional on reproduction / replication. Add synthetic data for later
```

# Ingest data

```{r warning=FALSE}
pilot_ds_tb <- ready4::get_table_from_loc_file(paste0(paths_ls$input_data_dir_1L_chr,
                                                       "/",
                                                       paths_ls$pilot_ds_fl_nm_1L_chr),
                                                heading_rows_1L_int = 3L,
                                                force_numeric_1L_lgl = T)
```

We can also retrieve details about the design of the pilot survey

```{r}
Y <- ingest(X,fls_to_ingest_chr = c("CCC_pilot_dce_design_ls","DDD_pilot_dce_design_ls"))
```
```{r}
if(reproduce_1L_lgl){
  dce_design_ls <- Y@b_Ready4useIngest@objects_ls$DDD_pilot_dce_design_ls
}else{
  dce_design_ls <- Y@b_Ready4useIngest@objects_ls$CCC_pilot_dce_design_ls
}
```

# Analyse data
We can now produce the analysis of the pilot survey data. Note that the analysis algorithm involves random sampling so a seed must be set to make results reproducible. Also, for some random seeds NULL values will be generated that will prevent the analysis executing in full. Changing the random seed and rerunning the code will address this.


```{r}
dce_design_ls <- add_design_spec(dce_design_ls,
                                 pilot_ds_tb = pilot_ds_tb,
                                 choice_var_pfx_1L_chr = "DCE_B",
                                 constraints_ls = list(Endorsers_non_expert = c(0.005, Inf),
                                                       Endorsers_expert = c(0.006, Inf),
                                                       Cost = c(-Inf, -0.0499)),
                                 draws_1L_int = 100L,
                                 seed_1L_int = 1985,
                                 set_idx_1L_int = 1L)
# Need to implement: https://stackoverflow.com/questions/69639782/installing-gfortran-on-macbook-with-apple-m1-chip-for-use-in-r
```

# Share work
The final step is to share our non-confidential work outputs with others in an online repository. Note, you will need to supply your own repository details to run this part of the code successfully as you will not have write permissions to the repository `X` that we specify below.

```{r eval = FALSE}
Y <- share(X,
           obj_to_share_xx = dce_design_ls,
           fl_nm_1L_chr = ifelse(reproduce_1L_lgl,"DDD_pupdated_dce_design_ls","CCC_updated_dce_design_ls"),
           description_1L_chr = paste0("DCE design specification post analysis of pilot data (output of dce_sa_design ",
                                       ifelse(reproduce_1L_lgl,"reproduction","replication")," program)"))
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->





