---
title: "Replicate Final Design"
output: html_document
date: '2022-10-19'
---

```{r child=if(T){"../Child_RMDs/_Set_Up.Rmd"}else{NULL}, eval=TRUE}
```
```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Copyright.Rmd"}else{NULL}, eval=TRUE}
```

\blandscape
<!---BLOCK_LANDSCAPE_START--->

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_About_Repln_Final_Des_Code.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Prepare_Workspace.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Custom_Functions_Text.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/XX_Funs.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Ingest_Analysis.Rmd"}else{NULL}, eval=TRUE}
```

# Update survey design
We now update the survey experimental design based on analysis of pilot survey results.

```{r}
if(reproduce_1L_lgl){
  dce_design_ls$efnt_dsn_ls <- append(dce_design_ls$efnt_dsn_ls,
                                    list(readRDS(file = paste0(paths_ls$output_data_dir_1L_chr,"/Archive/Design_Records/no_app_optout_ls.rds"))) %>% # Replace with DV ingest
                                          stats::setNames(paste0("Set_", length(dce_design_ls$efnt_dsn_ls) + 1)))
  }else{
    dce_design_ls <- add_design_spec(dce_design_ls,  priors_idx_1L_int = 1L, set_idx_1L_int = 1)
}
```

# Create choice cards for each block
We can now generate HTML choice cards for each block.

```{r warning=FALSE}
dce_design_ls <- add_design_spec(dce_design_ls,
                                 add_choice_cards_1L_lgl = T,
                                 block_idxs_ls = {if(reproduce_1L_lgl){
                                   list(as.integer(c(3,5,6,7,8,9,12,14,15,18,19,20,23,24,28)), 
                                    as.integer(setdiff(1:dce_design_ls$choice_sets_ls$nbr_of_sets_1L_int,
                                                       c(3,5,6,7,8,9,12,14,15,18,19,20,23,24,28)))) %>%
                                     stats::setNames(paste0(paste0("block_",1:2),"_int"))}else{list()}},
                                 transform_att_nms_1L_lgl = T)
```


# Preview survey
We can now preview all of our choice cards in an interactive Shiny app.

```{r eval=FALSE}
launch_survey_preview(dce_design_ls, block_1L_int = 1L)
```

```{r eval=FALSE}
launch_survey_preview(dce_design_ls, block_1L_int = 2L)
```


# Share work
The final step is to share our work with others in an online repository. Note, you will need to supply your own repository details to run this part of the code successfully as you will not have write permissions to the repository `X` that we specify below.

```{r eval = FALSE}
Y <- share(X,
           obj_to_share_xx = dce_design_ls,
           fl_nm_1L_chr = ifelse(reproduce_1L_lgl,"DDD_final_dce_design_ls","CCC_dce_design_ls"),
           description_1L_chr = paste0("DCE design specification for final version of survey - ",
                                       ifelse(reproduce_1L_lgl,"reproduction","replication")," (output of dce_sa_design program)"))
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->



