---
title: "Replicate Pilot Design"
output: html_document
date: '2022-10-19'
---

```{r child=if(T){"../Child_RMDs/_Set_Up.Rmd"}else{NULL}, eval=TRUE}
```
```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Copyright.Rmd"}else{NULL}, eval=TRUE}
```

\blandscape
<!---BLOCK_LANDSCAPE_START--->

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_About_Repln_Pilot_Des_Code.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Prepare_Workspace.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Custom_Functions_Text.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/XX_Funs.Rmd"}else{NULL}, eval=TRUE}
```

# Specify survey features and priors
Our first main step is to define the key features of the survey (attributes, levels, choice cards, blocks) and our prior expectation of the relative importance of attributes and levels.

## Specify choice attributes and levels
We can now define the attributes and levels for the choices to be included in the survey.

We begin by specifying the following features of our survey:

- the labels used for each choice card alternative; 

- the attributes and levels used to describe each alternative;

- the variable names we will use when converting factor attribute levels to dummy variables (reference levels do not need converting); 

- the short names we will use when plotting factor attribute levels; 

- which of the alternatives is a cost attribute, its currency and frequency of payment; and 

- which of the alternatives is an opt-out (no -choice) option.

```{r}
dce_design_ls <- add_design_spec(alternatives_chr = c("Social Anxiety App A", "Social Anxiety App B", "Do not use a social anxiety app"),
     att_lvls_tb = list(c("Outcomes","Information_sharing", "Social","Endorsers", "Cost"),
                        list(c("Provides knowledge and skills to  manage future situations",
                               "Addresses current symptoms",
                               "Addresses current symptoms and provides knowledge and skills to manage future situations"),
                             c("No information is shared with your treating clinician", 
                               "Information is shared with your treating clinician in accordance with app policy", 
                               "Information is shared with your treating clinician based on settings you control"),
                             c("No discussions with other app users",
                               "Unmoderated discussions with other app users",
                               "Discussions with other app users moderated by trained peers", 
                               "Discussions with other app users moderated by mental health clinicians", 
                               "Discussions with other app users moderated by both trained peers and mental health clinicians"),
                             c("App has no endorsers",
                               "App is endorsed by respected non experts",
                               "App is endorsed by youth mental health experts"), 
                             c(0,5,15,30,60)),
                        list(c(NA_character_,"curr_sym", "curr_sym_future_sit"), 
                             c(NA_character_,"app_policy","user_settings"),
                             c(NA_character_,"unmod_disc", "trained_peer_mod", "clinician_mod", "peer_clinician_mod"),
                             c(NA_character_,"non_expert","expert"),
                             NA_character_),
                        list(c("Future","Current", "Both"), 
                             c("None","App policy","User settings"),
                             c("None","Unmoderated", "Peer", "Clinician", "Both"),
                             c("None","Non-expert","Expert"),
                             "Cost")) %>%
       purrr::pmap_dfr(~ tibble::tibble(attribute_chr = ..1,
                                        level_chr = as.character(..2),
                                        continuous_lgl = is.numeric(..2),
                                        dummy_nm_chr = ..3,
                                        distribution_chr = "normal",
                                        short_nms_chr = ..4)),
     cost_att_idx_1L_int = 5L,
     cost_pfx_1L_chr = "$",
     cost_sfx_1L_chr = " per month",
     opt_out_idx_1L_int = 3L,
     session_ls = session_ls)  
```

## Create candidate choices matrix
We now create a design matrix of the full factorial of all attribute / level combinations. To do this we create a list specifying the number of attributes for each level and record whether coefficients for each attribute are Continuous ("C" ) or Dummy ("D").

```{r}
dce_design_ls <- add_design_spec(dce_design_ls,
                                 add_cndt_design_mat = T)
```

## Specifiy additional features about our survey
We now provide additional detail about our intended survey design, specifying:

- the total number of choice cards; and
- the number of survey blocks.

```{r}
dce_design_ls <- add_design_spec(dce_design_ls,
                                 nbr_of_sets_1L_int = 30,
                                 nbr_of_blocks_1L_int = 2)
```

## Create matrices of parameter value draws based on prior expectations
We now specify our prior expectation of the values of coefficients for each attribute and an opt out constant. The coefficients supplied in this section were based on study authors' perception of participant feedback at a number of focus groups. We request that 10 values for each parameter be generated and supply a seed value for reproducibility. As this design includes an opt-out alternative, the following command will create two matrices of parameter values: one for the alternative specific constant, the other for the coefficients.

```{r}
dce_design_ls <- add_design_spec(dce_design_ls,
                                 draws_1L_int = 10L,  
                                 priors_dbl = c(-0.15, # Opt-out constant
                                                0.5,1, # Outcomes
                                                0.2,0.4, # Information sharing
                                                0.1,0.2,0.3,0.4, # Social
                                                0.1,0.2,# Endorsers
                                                -0.05),
                                 seed_1L_int = 1987L) # Cost
```

# Create efficient pilot survey design

We can now create the initial efficient design to be used in the pilot survey. Note this step can take a long time (about an hour).

```{r}
if(reproduce_1L_lgl){
  dce_design_ls$efnt_dsn_ls <- append(dce_design_ls$efnt_dsn_ls,
                                    list(ingest(X, fls_to_ingest_chr = c("AAA_pilot_design_ls"), metadata_1L_lgl = F) %>% purrr::pluck("pilot_design_ls")) %>%
                                          stats::setNames(paste0("Set_", length(dce_design_ls$efnt_dsn_ls) + 1)))
  }else{
    dce_design_ls <- add_design_spec(dce_design_ls,  priors_idx_1L_int = 1L)
}
```

# Create choice cards for each block
We can now generate HTML choice cards for each block.

```{r warning=FALSE}
dce_design_ls <- add_design_spec(dce_design_ls,
                                 add_choice_cards_1L_lgl = T,
                                 transform_att_nms_1L_lgl = T)
```

# Preview survey
We can now preview all of our choice cards in an interactive Shiny app.

```{r eval=FALSE}
launch_survey_preview(dce_design_ls, block_1L_int = 1L)
```

```{r eval=FALSE}
launch_survey_preview(dce_design_ls, block_1L_int = 2L)
```

# Share work
The final step is to share our work with others in an online repository. Note, you will need to have previously supplied values for `X` that correspond to a repository for which you have write permissions to run this part of the code successfully.

```{r eval = FALSE}
Y <- share(X,
           obj_to_share_xx = dce_design_ls,
           fl_nm_1L_chr = ifelse(reproduce_1L_lgl,"DDD_pilot_dce_design_ls","CCC_pilot_dce_design_ls"),
           description_1L_chr = paste0("Pilot survey design specification - ",
                                       ifelse(reproduce_1L_lgl,"reproduction","replication")," (output of dce_sa_design program)"))
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->



