---
title: "Replicate Final Design"
output: html_document
date: '2022-10-19'
---

```{r child=if(T){"../Child_RMDs/_Set_Up.Rmd"}else{NULL}, eval=TRUE}
```
```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Copyright.Rmd"}else{NULL}, eval=TRUE}
```

\blandscape
<!---BLOCK_LANDSCAPE_START--->

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_About_Repln_Final_Des_Code.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Prepare_Workspace.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Custom_Functions_Text.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/XX_Funs.Rmd"}else{NULL}, eval=TRUE}
```

# Retrieve pilot survey design
We retrieve details about the design of the pilot survey.

```{r echo=params$is_subroutine_lgl, eval=params$is_subroutine_lgl}
dce_design_ls <- ingest(X,
                        fls_to_ingest_chr = ifelse(reproduce_1L_lgl,
                                                     "DDD_updated_dce_design_ls","CCC_updated_dce_design_ls"),
                        metadata_1L_lgl = F)
```

# Update survey design
We now update the survey experimental design based on analysis of pilot survey results.

```{r}
if(reproduce_1L_lgl){
  dce_design_ls$efnt_dsn_ls <- append(dce_design_ls$efnt_dsn_ls,
                                    list(readRDS(file = paste0(paths_ls$output_data_dir_1L_chr,"/Archive/Design_Records/no_app_optout_ls.rds"))) %>% # Replace with DV ingest
                                          stats::setNames(paste0("Set_", length(dce_design_ls$efnt_dsn_ls) + 1)))
  }else{
    dce_design_ls <- add_design_spec(dce_design_ls,  priors_idx_1L_int = 1L,set_idx_1L_int = 1)
}
```

# Create choice cards for each block
We can now generate HTML choice cards for each block.

```{r warning=FALSE}
dce_design_ls <- add_design_spec(dce_design_ls,
                                 block_idxs_ls = {if(reproduce_1L_lgl){
                                   list(as.integer(c(3,5,6,7,8,9,12,14,15,18,19,20,23,24,28)), 
                                    as.integer(setdiff(1:dce_design_ls$choice_sets_ls$nbr_of_sets_1L_int,
                                                       c(3,5,6,7,8,9,12,14,15,18,19,20,23,24,28)))) %>%
                                     stats::setNames(paste0(paste0("block_",1:2),"_int"))}else{list()}},
                                 set_idx_1L_int = 2L,
                                 transform_att_nms_1L_lgl = T)
```


# Preview survey
We can now preview all of our choice cards in an interactive Shiny app.

```{r eval=FALSE}
launch_survey_preview(dce_design_ls, set_idx_1L_int = 2L, block_1L_int = 1L)
```

```{r eval=FALSE}
launch_survey_preview(dce_design_ls, set_idx_1L_int = 3L, block_1L_int = 2L)
```


# Share work
The final step is to share our work with others in an online repository. Note, you will need to supply your own repository details to run this part of the code successfully as you will not have write permissions to the repository `X` that we specify below.

```{r eval = FALSE}
Y <- share(X,
           obj_to_share_xx = list(choice_cards_final_ls = choice_cards_final_ls,
                                  final_survey_ls = final_survey_ls),
           fl_nm_1L_chr = "BBB_final_design_repln_ls", # MODIFY
           description_1L_chr = "List object to help replicate pilot survey (output of dce_sa_design replication program)")
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->



