---
title: "Replicate Final Design"
output: html_document
date: '2022-10-19'
---

```{r child=if(T){"../Child_RMDs/_Set_Up.Rmd"}else{NULL}, eval=TRUE}
```
```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Copyright.Rmd"}else{NULL}, eval=TRUE}
```

\blandscape
<!---BLOCK_LANDSCAPE_START--->

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_About_Repln_Final_Des_Code.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Prepare_Workspace.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(F){"../Child_RMDs/_Custom_Functions_Text.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_XX_Funs_Replication.Rmd"}else{NULL}, eval=TRUE}
```

```{r child=if(params$is_subroutine_lgl){"../Child_RMDs/_Ingest_Analysis.Rmd"}else{NULL}, eval=TRUE}
```

# Update survey design
We now update the survey experimental design based on analysis of pilot survey results.

```{r}
if(reproduce_1L_lgl){
  dce_design_ls$efnt_dsn_ls <- append(dce_design_ls$efnt_dsn_ls,
                                    list(readRDS(file = paste0(paths_ls$output_data_dir_1L_chr,
                                                               "/Archive/Design_Records/no_app_optout_ls.rds"))) %>% # Replace with DV ingest
                                          stats::setNames(paste0("Set_", length(dce_design_ls$efnt_dsn_ls) + 1)))
  }else{
    dce_design_ls <- add_design_spec(dce_design_ls,  priors_idx_1L_int = 1L, set_idx_1L_int = 1)
}
```

# Create final survey HTML choice cards
We can now generate HTML choice cards for each block of the final survey.

```{r warning=FALSE}
dce_design_ls <- add_design_spec(dce_design_ls,
                                 add_choice_cards_1L_lgl = T,
                                 block_idxs_ls = {if(reproduce_1L_lgl){
                                   list(as.integer(c(3,5,6,7,8,9,12,14,15,18,19,20,23,24,28)), 
                                    as.integer(setdiff(1:dce_design_ls$choice_sets_ls$nbr_of_sets_1L_int,
                                                       c(3,5,6,7,8,9,12,14,15,18,19,20,23,24,28)))) %>%
                                     stats::setNames(paste0(paste0("block_",1:2),"_int"))}else{list()}},
                                 transform_att_nms_1L_lgl = T)
```


# Preview final survey
We can now preview all of our choice cards in an interactive Shiny app.

```{r eval=FALSE}
launch_survey_preview(dce_design_ls, block_1L_int = 1L)
```

```{r eval=FALSE}
launch_survey_preview(dce_design_ls, block_1L_int = 2L)
```

# Share work
The final step is to share our work with others in an online repository. Note, if you don't have write permissions for `X`, you should replace `X` with an alternative `Ready4useRepos` object that provides details of a repository for which you have write permissions.

```{r eval = FALSE}
Y <- share(X,
           obj_to_share_xx = dce_design_ls,
           fl_nm_1L_chr = ifelse(reproduce_1L_lgl,"DDD_final_dce_design_ls","CCC_dce_design_ls"),
           description_1L_chr = paste0("DCE design specification for final version of survey - ",
                                       ifelse(reproduce_1L_lgl,"reproduction","replication")," (output of dce_sa_design program)"))
```

\elandscape
<!---BLOCK_LANDSCAPE_STOP--->



